Template for preparing your Brief Report submission to PNAS using Overleaf

### 2023-11-22 PNAS/index.Rnw
Tweaking the introduction

As we develop objective algorithms and standardize laboratory procedures in forensic pattern evidence, we must remain cognizant that we often are conducting many comparisons, either implicitly or explicitly. Algorithms in pattern evidence often utilize cross-correlation \citep{vorburgerApplicationsCrosscorrelationFunctions2011} to align different data sources, implicitly making comparisons along the entire length or surface of the data. Similarly, forensic examiners visually rotate or align two pieces of evidence under comparison microscopes. When we conduct database searches, these searches often return the $N$ best matches from the database, but this requires making comparisons to all of the database entries which meet the search criteria.

Partial matches in fingerprint evidence have been shown to be problematic XXX cite XXX, and the AFIS database search conducted while investigating the Madrid bombing in 2004 was one factor cited in the inquiry into the false accusation of Brandon Mayfield. As forensic intelligence databases in other disciplines are implemented (such as IBIS in firearms), we must confront the issues with multiple comparisons and false positive rates before more embarrassing false accusations lead the public to question the validity of forensic science.

In this paper, we consider the multiple comparisons problems that arise from a relatively simple toolmark comparison: matching a cut wire to a wire-cutting tool. We describe the approach and calculate the number of comparisons performed, and then assess the likelihood of a false positive error under multiple comparisons using rates from published black-box studies.

>>>>

As we develop objective algorithms and standardize laboratory procedures in forensic pattern evidence, we must remain cognizant that we often are conducting many comparisons, either implicitly or explicitly. Algorithms in pattern evidence often utilize cross-correlation \citep{vorburgerApplicationsCrosscorrelationFunctions2011} to align different data sources, implicitly making comparisons along the entire length or surface of the data. Similarly, forensic examiners visually rotate or align two pieces of evidence under comparison microscopes. Similarly, when we conduct database searches, these searches often return the $N$ best matches from the database, but this requires making comparisons to all of the database entries which meet the search criteria.

The multiple comparison problems in forensics are distinct from the familywise error rate and false discovery rate problems that have been previously addressed in major ways: our tests are sequential, not concurrent, with dependencies depending on both the testing procedure and the data. In addition, an identification might be sufficient to end the search; as a result, this problem is more akin to a ``search until you find" problem than a situation where a family-wise error rate or false discovery rate is applicable - we are interested in the probability of at least one error in a series of sequential comparisons.

The multiple testing problem is closely related to issues which have caused embarrassing false accusations and mistrust of forensic pattern evidence: partial matches and database searches. As we assemble research databases for explicitly making many comparisons and tackle problems which implicitly involve multiple comparisons, we must confront these issues before more embarrassing missteps lead the public to question the validity of forensic science.

In this paper, we consider the multiple comparisons problem that arises from a relatively simple toolmark comparison: matching a cut wire to a wire-cutting tool. We describe the approach and calculate the number of comparisons performed, and then assess the likelihood of a false positive error considering the multiple comparisons performed, using error rates derived from published black-box studies.
